07-logistic_regression

### 2019-02-26 journals/07-logistic_regression/07-logistic_regression.Rmd
fixed issues with logistic regressions

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE, 
                      cache = TRUE)
```

@@

# Logistic Regression Model

```{r eval = FALSE}
# Fit a logistic regression model with only main effects
logit <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + matches + 
                        mismatches + cms + non_cms + sum_peaks,
            data = hamby173and252_train, 
            method = "glm", 
            family = "binomial")

summary(logit)

logit_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                    model = logit)

logit_explain <- explain(x = hamby224_test %>% select(rf_features) %>% na.omit(), 
                          explainer = logit_lime, 
                          n_labels = 1,
                          n_features = 3)

plot_features(logit_explain[1:12,])
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

@@

# Logistic Regression Models

### Main Effects Only

The code below fits a logistic regression model to the training data using the `train` function from the caret package. The nine features used to fit `rtrees` are included as main effects only. The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.

```{r}
# Fit or load the logistic regression model with only main effects
if(!file.exists("../../data/logistic_mains.rds")) {

  # Fit the model
  logistic_mains <- caret::train(as.factor(samesource) ~ ccf + rough_cor + D + sd_D + 
                                   matches + mismatches + cms + non_cms + sum_peaks,
                                 preProcess = "scale",
                                 data = hamby173and252_train, 
                                 method = "glm", 
                                 family = "binomial")

  # Save the model
  saveRDS(logistic_mains, "../../data/logistic_mains.rds")

} else{

  # Load the model
  logistic_mains <- readRDS("../../data/logistic_mains.rds")

}
```

The output from the model is shown below. The features of ccf and matches stand out as the most important features in the model.

```{r}
# Summary of the model
summary(logistic_mains)
```

### All Two Way Interactions

The code below fits a logistic regression model to the training data using the `train` function from the caret package. The nine features used to fit `rtrees` are included as main effects and with all two way interactions. The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.

```{r}
# Fit or load the logistic regression model with all two way interactions
if(!file.exists("../../data/logistic_inters2.rds")) {

  # Fit the model
  logistic_inters2 <- caret::train(as.factor(samesource) ~
                                       (ccf + rough_cor + D + sd_D + matches + 
                                          mismatches + cms + non_cms + sum_peaks)^2,
                                     preProcess = "scale",
                                     data = hamby173and252_train,
                                     method = "glm", 
                                     family = "binomial")

  # Save the model
  saveRDS(logistic_inters2, "../../data/logistic_inters2.rds")

} else{

   # Load the model
  logistic_inters2 <- readRDS("../../data/logistic_inters2.rds")

}
```

The output from the model is shown below.

```{r}
# Summary of the model
summary(logistic_inters2)
```

### All Three Way Interactions

The code below fits a logistic regression model to the training data using the `train` function from the caret package. The nine features used to fit `rtrees` are included as main effects and with all two and three way interactions. The features are standardized prior to fitting the model using the `preProcess = "scale"` in `train`.

```{r eval = FALSE}
# Fit or load the logistic regression model with all two and three way interactions
if(!file.exists("../../data/logistic_inters3.rds")) {

  # Fit the model
  logistic_inters3 <- caret::train(as.factor(samesource) ~
                                       (ccf + rough_cor + D + sd_D + matches + 
                                          mismatches + cms + non_cms + sum_peaks)^3,
                                     preProcess = "scale",
                                     data = hamby173and252_train,
                                     method = "glm", 
                                     family = "binomial")

  # Save the model
  saveRDS(logistic_inters3, "../../data/logistic_inters3.rds")

} else{

  # Load the model
  logistic_inters3 <- readRDS("../../data/logistic_inters3.rds")

}
```

The output from the model is shown below.

```{r eval = FALSE}
# Summary of the model
summary(logistic_inters3)
```

### Comparing the Logistic Models

# Applying LIME to the Models

### Main Effects Only

```{r eval = FALSE}
logistic_mains_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                            model = logistic_mains$finalModel)

logistic_mains_explain <- explain(x = hamby224_test %>% 
                                    select(rf_features) %>% 
                                    na.omit(), 
                                  explainer = logistic_mains_lime, 
                                  n_labels = 1,
                                  n_features = 3)

plot_features(logistic_mains_explain[1:12,])
```

### All Two Way Interactions

```{r eval = FALSE}
logistic_inters2_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                              model = logistic_inters2)

logistic_inters2_explain <- explain(x = hamby224_test %>% 
                                      select(rf_features) %>% 
                                      na.omit(), 
                                    explainer = logistic_inters2_lime, 
                                    n_labels = 1,
                                    n_features = 3)

plot_features(logistic_inters2_explain[1:12,])
```

### All Three Way Interactions

```{r eval = FALSE}
logistic_inters3_lime <- lime(x = hamby173and252_train %>% select(rf_features), 
                              model = logistic_inters3)

logistic_inters3_explain <- explain(x = hamby224_test %>% 
                                      select(rf_features) %>% 
                                      na.omit(), 
                                    explainer = logistic_inters3_lime, 
                                    n_labels = 1,
                                    n_features = 3)

plot_features(logistic_inters3_explain[1:12,])
```

# Session Info

```{r}
sessionInfo()
```
